Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2021-12-16 SCCAbstract_SDSS2022-knitr.Rnw
A few comments

% File SDSS2020_SampleExtendedAbstract.tex
\documentclass[10pt]{article}
\usepackage{newtxtext, newtxmath, times}
\usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath, amsfonts}
\usepackage{algorithm, algorithmic}  
\usepackage{graphicx}

@@

\begin{quotation}
\small A visual display of the most important information needed to achieve one or more objectives, consolidated and arranged on a single screen so the information can be monitored at a glance. \cite{few}
\end{quotation}

Some communities continue to thrive as they lose population because they adapt and stay focused on quality of life, community services, and investing in the future. This is what we call rural smart shrinkage. Our research team is developing strategies and sharing examples of successful shrink-smart towns to help similar communities to improve quality of life for their residents \cite{scc}. Our work focuses on developing and challenges novice analysts in advanced statistical concepts and data visualizations to help make decisions. Specifically, what data can be used to help make decisions, what strategies overcome the challenges of those analysts feel empowered to make data-driven decisions. Our ultimate aim is to help inform Iowa's Rural Shrink Smart communities by using effective dashboards to help those towns build the Quality of Life (QoL) Measures.

>>>>

% File SDSS2020_SampleExtendedAbstract.tex
\documentclass[10pt]{article}
\usepackage{newtxtext, newtxmath, times}
\usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath, amsfonts}
\usepackage{algorithm, algorithmic}  
\usepackage{graphicx}
% Commands for editing
\newcommand{\db}[1]{{\textcolor{orange}{#1}}}
\newcommand{\svp}[1]{{\textcolor{blue}{#1}}}

@@

\begin{quotation}% I don't know that we need this... dashboards are very common, so let's focus on the problem and the dashboard as an obvious solution.
\small A visual display of the most important information needed to achieve one or more objectives, consolidated and arranged on a single screen so the information can be monitored at a glance. \cite{few}
\end{quotation}

Some communities continue to thrive as they lose population because they adapt\svp{, maintaining quality of life and community services for residents while} investing in the future. % putting sentences on different lines helps with git merges and also makes it easier to figure out where {} match up :)
\svp{This process,} \emph{smart shrinkage}\svp{, is important for rural areas who have experienced shrinking populations for decades.} 
\svp{As small rural towns do not have access to data scientists or even the ability to easily leverage data collected locally to support decisions, our} research team \svp{will provide communities with data about services in small town Iowa in order to assist with} developing strategies to improve quality of life for their residents amid shrinking populations \cite{scc}. \svp{We hope to allow towns to discover their own data and compare to other similar towns, centering decision-making on data in the context of small-town Iowa life. In the process, we will assess our visualizations to determine which strategies for user interface and interactive graphics design are most useful to empower town leaders to make discoveries in publicly available data assembled with a focus on items that impact rural quality of life.}
% Our work focuses on developing and challenges novice analysts in advanced statistical concepts and data visualizations to help make decisions. Specifically, what data can be used to help make decisions, what strategies overcome the challenges of those analysts feel empowered to make data-driven decisions. Our ultimate aim is to help inform Iowa's Rural Shrink Smart communities by using effective dashboards to help those towns build the Quality of Life (QoL) Measures.
